RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface

### 2023-08-12 main.tex
:speech_balloon: Fix label font

		\begin{subsubsection}{Primary \gls{snr}}
			\label{sc:primary_snr}
			The backscatter \gls{snr} is fixed to \qty{0}{dB} in this study.
			Interestingly, Fig.~\subref*{fg:region_snr_primary} shows that increasing the primary \gls{snr} can improve the primary rate but degrade the backscatter rate.
			The reason is that the relative strength of the scattered signal compared to the direct signal is weakened, such that the nodes cannot make enough difference to the energy detector.
			This, together with Fig.~\subref*{fg:region_beamforming} and \subref*{fg:region_tags}, emphasizes the importance of balancing the primary and backscatter \gls{snr} in the design of active-passive coexisting networks.
			% This, together with Fig.~\subref*{fg:region_beamforming} and \subref*{fg:region_tags}, emphasizes the importance of primary-backscatter tradeoff in active-passive coexisting networks.
		\end{subsubsection}

		\begin{subsubsection}{Backscatter \gls{snr}}
			The primary \gls{snr} is fixed to \qty{20}{dB} in this study.
			Fig.~\subref*{fg:region_snr_backscatter} shows that the primary and backscatter rates are both improved when the backscatter \gls{snr} increases.
			This motivates one to use high-efficiency or semi-passive RIScatter nodes to improve the overall performance.
			In a multi-user RIScatter network, each node may be assigned to the nearest user to guarantee uniformly good performance for both links.
		\end{subsubsection}
	\end{subsection}
\end{section}

>>>>

		\begin{subsubsection}{Primary \gls{snr}}
			\label{sc:primary_snr}
			The backscatter \gls{snr} is fixed to \qty{0}{dB} with $Q=1$ in this study.
			Interestingly, Fig.~\subref*{fg:region_snr_primary} shows that increasing the primary \gls{snr} can improve the primary rate but degrade the backscatter rate.
			The reason is that the relative strength of the scattered signal compared to the direct signal is weakened, such that the nodes cannot make enough difference to the energy detector.
			This, together with Fig.~\subref*{fg:region_beamforming} and \subref*{fg:region_tags}, emphasizes the importance of balancing the primary and backscatter \gls{snr} in the design of active-passive coexisting networks.
			% This, together with Fig.~\subref*{fg:region_beamforming} and \subref*{fg:region_tags}, emphasizes the importance of primary-backscatter tradeoff in active-passive coexisting networks.
		\end{subsubsection}

		\begin{subsubsection}{Backscatter \gls{snr}}
			The primary \gls{snr} is fixed to \qty{20}{dB} with $Q=1$ in this study.
			Fig.~\subref*{fg:region_snr_backscatter} shows that the primary and backscatter rates are both improved when the backscatter \gls{snr} increases.
			This motivates one to use high-efficiency or semi-passive RIScatter nodes to improve the overall performance.
			In a multi-user RIScatter network, each node may be assigned to the nearest user to guarantee uniformly good performance for both links.
		\end{subsubsection}
	\end{subsection}
\end{section}
